---
title: Title here
subtitle: Do you have a subtitle? If so, write it here
titlerunning: Short form of title (if too long for head)
authorrunning: Short form of author list if too long for running head
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Äüthör 1
  address: Department of YYY, University of XXX
  email: abc@def
  
- name: Âuthóř 2
  address: Department of ZZZ, University of WWW
  email: djf@wef

keywords:
- key
- dictionary
- word

#PACS: 
#- PAC1
#- superPAC
    
MSC:
- MSC code 1
- MSC code 2

abstract: |
  The text of your abstract.  150 -- 250 words.

bibliography: bibliography.bib
biblio-style: spphys
# bibstyle options spbasic(default), spphys, spmpsci
#output: html_notebook
output: rticles::springer_article

---

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)

# I usually load my libraries up front to keep things organized
library(rticles)
library(bookdown)
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggthemes)
library(ggExtra)
library(dplyr)
library(stringr)

```


# Introduction {#intro}

Your text comes here. Separate text sections with \cite{Mislevy06Cog}.

# Section title {#sec:1}

Text with citations by \cite{Galyardt14mmm}.

## Subsection title {#sec:2}

as required. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:1}).

#### Paragraph headings 

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}








# ---Instructions---

* Headers are specified with #, ##, ###, etc. for H1, H2, H3, etc.
* When you would like to cite a paper, your citation looks like this: "[@Key]" - e.g. [@author2017]
* If you would like to add a figure, this can be done with an R snippet:
```{r figRef, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure caption here"}
## R code here, with plot output at end, for example using ggplot2

```

* To cross-reference figures in your text, simply write something like: As shown in Figure  \@ref(fig:figRef) ...
* Tables can be added using the kable function from knitr, for example:
```{r tabRef, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}

#df <- read.csv(...)

#knitr::kable(df, caption = "Table caption here...", booktabs = TRUE)
```

* Cross-referencing a Table is similar to that of a Figure. For example: Table \@ref(tab:tabRef) shows the data...
* Put #References at the end of your document to generate the bibliography.
* And don't forget to have a look here for more resources: http://rmarkdown.rstudio.com/

More info: http://landscapeportal.org/blog/2017/09/06/r-markdown-template-for-a-scientific-manuscript/
